A Survey of Near-Term Exoskeleton Technology\\ (Draft 4.0)

### 2015-09-30 control.tex
more updates

What to do about this to achieve robust online optimalization-based control is
currently a research issue. In actual implementations, skilled engineers manually
tune optimization weights and the various constraints that are active to
make this type of control work reliably. The fact that this has been done on many actual
humanoid robots in many situations is comforting. The fact that none of these
implementations have moved with the speed and agility of a top percentile
human athlete is disconcerting.

@@

{\it [Exoskeletons] have the implicit property
of causing a virtual modification of the dynamic response of
the human limb. We use this property of the exoskeletons
action to formulate a unified control design framework called
Integral Admittance [torque to angle] Shaping, which designs exoskeleton con-
trollers capable of producing the desired dynamic response
for the assisted limb. In this framework, a virtual increase
in the admittance of the limb is produced by coupling it
to an exoskeleton that exhibits active behavior. Specifically,
our framework shapes the magnitude profile of the integral
admittance (i.e. torque-to-angle relationship) of the coupled
human-exoskeleton system, such that the desired assistance is
achieved. This framework also ensures that the coupled stability
and passivity are guaranteed.}
%~\cite{Nagarajan_etal_2015}

>>>>

What to do about this to achieve robust online optimization-based control is
currently a research issue. In actual implementations, skilled engineers manually
tune optimization weights and the various constraints that are active to
make this type of control work reliably. The fact that this has been done on many actual
humanoid robots in many situations is comforting. The fact that none of these
implementations have moved with the speed and agility of a top percentile
human athlete is disconcerting.

@@

{\it [Exoskeletons] have the implicit property
of causing a virtual modification of the dynamic response of
the human limb. We use this property of the exoskeletons
action to formulate a unified control design framework called
Integral Admittance [torque to angle] Shaping, which designs exoskeleton 
controllers capable of producing the desired dynamic response
for the assisted limb. In this framework, a virtual increase
in the admittance of the limb is produced by coupling it
to an exoskeleton that exhibits active behavior. Specifically,
our framework shapes the magnitude profile of the integral
admittance (i.e. torque-to-angle relationship) of the coupled
human-exoskeleton system, such that the desired assistance is
achieved. This framework also ensures that the coupled stability
and passivity are guaranteed.}
%~\cite{Nagarajan_etal_2015}

### 2015-09-30 intent.tex
more updates

@@

Here is an example of a robot seeing and moving faster than a human, and
consistantly beating a human opponent in rock-paper-scissors.\\
\url{https://www.youtube.com/watch?v=Qb5UIPeFClM&feature=player_embedded}

@@

Muscle electrical activity can be measured by surface electrodes
(not very specific to particular muscles), needle electrodes (painful,
especially during movement), and implanted electrodes.\\
\url{http://www.medscape.com/viewarticle/542356_2}.\\
Typical processing is to 
high-pass filter at 20 Hz, rectify, low-pass filter at 6 Hz,
offset by a small value, and amplify by some scaling factor
to get a muscle activation estimate.\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7139980}\\
One can apply pattern recogntion to this signal.\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7222568}\\

@@

We have a cooperative operator, who can signal using unused frequency
ranges or patterns on existing measurement
channels (brain signals, EMG, force, and motion) or use 
task specific intefaces such as built-in keyboards, touch sensors, joysticks,
and speech recognition.
Operators can resolve ambiguities, select behaviors, and indicate
parameterization (how far, how high, how fast) using these interfaces.

We note that the operator will use more command channels that just
body movement, since
the operator controls more than the pose and motion of the
exoskeleton. What if there are ``pointing'' sensors or communication
devices that need to be aimed at or track an area of interest? What if
there are additional (physical or virtual) pan/tilt/zoom cameras
pointing to the side and rear or line of sight secure communications,
for example. What about other controls, such as power assist level or
thermal control? It is an open question
how an operator can naturally express intent and
control these additional degress of freedom.

>>>>

\section{Clickable web links}

The web links (URLs) below can be clicked on to view, if your PDF viewer/browser supports that. On our browsers you actually have to click on the black
part of a letter, not just in the blue box (if present).

@@

Here is an example of a robot seeing and moving faster than a human, and
consistently beating a human opponent in rock-paper-scissors.\\
\url{https://www.youtube.com/watch?v=Qb5UIPeFClM&feature=player_embedded}

@@

Muscle electrical activity can be measured by surface electrodes
(not very specific to particular muscles), needle electrodes (painful,
especially during movement), and implanted electrodes.\\
\url{http://www.medscape.com/viewarticle/542356_2}.\\
Typical processing is to 
high-pass filter at 20 Hz, rectify, low-pass filter at 6 Hz,
offset by a small value, and amplify by some scaling factor
to get a muscle activation estimate.\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7139980}\\
One can apply pattern recognition to this signal.\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7222568}\\

@@

We have a cooperative operator, who can signal using unused frequency
ranges or patterns on existing measurement
channels (brain signals, EMG, force, and motion) or use 
task specific interfaces such as built-in keyboards, touch sensors, joysticks,
and speech recognition.
Operators can resolve ambiguities, select behaviors, and indicate
parameterization (how far, how high, how fast) using these interfaces.

We note that the operator will use more command channels that just
body movement, since
the operator controls more than the pose and motion of the
exoskeleton. What if there are ``pointing'' sensors or communication
devices that need to be aimed at or track an area of interest? What if
there are additional (physical or virtual) pan/tilt/zoom cameras
pointing to the side and rear or line of sight secure communications,
for example. What about other controls, such as power assist level or
thermal control? It is an open question
how an operator can naturally express intent and
control these additional degrees of freedom.

### 2015-09-30 technology.tex
more updates

Energy storage and actuation for superhuman manueverability.\\
\url{http://www.ncbi.nlm.nih.gov/pubmed/22169384}\\
\url{http://www.ric.org/app/files/public/4898/LemusVallery_GyroscopicBackpack_EMBC2014pdf.pdf}

@@

We can consider the following combinaitons:
\begin{itemize}
\item
series combinations - fast but weak actuator needs to hit range limit and then be strong. (leads to chattering) or just lock in position to exert big force
\item
parallel combination - strong but slow actuator needs to clutch out of circuit to move fast
\end{itemize}

>>>>

Energy storage and actuation for superhuman maneuverability.\\
\url{http://www.ncbi.nlm.nih.gov/pubmed/22169384}\\
\url{http://www.ric.org/app/files/public/4898/LemusVallery_GyroscopicBackpack_EMBC2014pdf.pdf}

@@

We can consider the following combinatons:
\begin{itemize}
\item
series - fast but weak actuator needs to hit range limit and then be strong. (leads to chattering) or just lock in position to exert big force
\item
parallel - strong but slow actuator needs to clutch out of circuit to move fast
\end{itemize}
